Who introduced the bug? The importance of the previous commit

### 2016-01-26 paperMSR.tex
SOme changes

\section{Introduction}
\label{sec:introduction}
How to plan to apply the knowledge in a way that can benefit software engineers.
What are the anticipated contributions of the work?  How will you evaluate them to demonstrate usefulness?

In order to investigate if this assumption is valid, we formulate following research questions:
\begin{itemize}
    \item RQ1 : How can tickets which are bug reports be differentiated from those that are not?
    \item RQ2:  How often is the bug caused in the previous commit?
\end{itemize}

The remainder of this paper is structured as follows; first, we discuss how to extract and classify data from specific repository of OpenStack in Section~\ref{}. In this repository we can find tickets that describe bugs; however, in order to obtain a successful results, we need know how many of them are bug reports. This problem is solved in Subsection~\ref{}, answering in this way RQ1. After having discriminated bug reports from those that are not, to answer the RQ2 we have calculated how many times the cause of the bug could be attributed to the previous commit (see Subsection~\ref{subsec:second}). Results are then shown in Section~\ref{}. Finally, we present a discussion, including the threats to validity, in Section~\ref{}.

@@

@@

@@

@@

\subsubsection{The Tool}
\label{sec:tool}
The tool was designed to solve the problem of missclassified, providing the researcher with all the relevant information needed to decide if an issue belongs to a bug report or not. The tool extracts automatically tickets from the project's repository, and offers a web-based interface which allows for collaboration, traceability and transparency of the identification of bug reports.

@@

We analyzed a total of 209 tickets in which there were 348 previous commit, which we had to classify into one of the following groups:
\begin{enumerate}
  \item It is responsible,
  \item It is not responsible,
  \item Undecided.
\end{enumerate}

@@

To analyze the lines of the files involved, we used therefore the \texttt{diff} command to display line-by-line difference between the file before and after the bug fix commit. \texttt{diff} is well-known algorithm, extensively explained in the research literature~\cite{ukkonen1985algorithms,myers1986ano}, which is included in any source code management system. \texttt{diff} examines both files and returns the differences found between them, showing the line number.% the necessary modifications which should be done in order to the files match. the differences found between them,showing the line number. %FIXME: de aqui en adelante no entiendo la frase. need to be made for first file and second file to match, that is, returns the differences found between them.

At this stage, we got a list with all the previous commits, which could be where the bug was introduced. We have to identify those previous commits responsible for inserting the line with the bug. When there are more than one commit implicated in the same file is because the bug was inserted in different lines of different commits, but not everyone has to be responsible for the commit, after the analysis the responsible can be only one of them or maybe two, in fact sometimes all of them were responsible. Therefore, comparing the status of the file, before and after the commit, we are be able to identify those previous commits that are responsible and those that are not, answering the RQ2.

After anlayzed all the previous commit involved in the 209 Bug reports, we have discovered that not all the previous commits were responsibles to cause the bug.
\subsubsection{Discarting False Positives}
\label{sec:discarting}
We have to discart these previous commits that change the format, that add blank spaces, that change comments and that copied lines from the previous commit but.

\begin{table}[htb]
\begin{center} {\footnotesize
\caption{ Probability of cause the bug depending on how many previous commits had the bug report}
\label{secondStage}
\begin{tabular}{lcc}
\toprule[0.3mm]
  & \multicolumn{1}{c}{After } & \multicolumn{1}{c}{Before} \\
  & \multicolumn{1}{c}{False Negative} & \multicolumn{1}{c}{False Negative} \\\hline
\raisebox{1ex}{Responsible} & 152 & 152 \\[0ex]
\raisebox{1ex}{Not responsible} & 154 & 114 \\[0ex]
\raisebox{1ex}{Undecided} & 42 & 42 \\[0ex]
\bottomrule[0.3mm]
\end{tabular} }
\end{center}
\end{table}

@@

\subsection{Fist Stage}
\label{sec:resultsFS}

We have manually analyzed 459 different tickets with support of the present tool, 125 from Cinder, 125 fron Nova, 125 from Horizon and 84 from Neutron. The table \ref{tab:1} show the percentage of each researcher after analyzing the tickets, 417 tickets were analyzed by two different researchers,

@@

58 tickets with more than one previous commit and 
\begin{table}[htb]
\begin{center} {\footnotesize
\caption{ Probability of cause the bug depending on how many previous commits had the bug report}
\label{secondStage}
\begin{tabular}{lcc}
\toprule[0.3mm]
  & \multicolumn{1}{c}{One previous } & \multicolumn{1}{c}{More than one previous} \\
  & \multicolumn{1}{c}{commit} & \multicolumn{1}{c}{commit} \\\hline
\raisebox{1ex}{Responsible} & 75.86\% & 46.32\% \\[0ex]
\raisebox{1ex}{Not responsible} & 6.9\% & 44.21\%\\[0ex]
\raisebox{1ex}{Undecided} & 17.24\% & 9.47\%\\[0ex]
\bottomrule[0.3mm]
\end{tabular} }
\end{center}
\end{table}

@@

\subsection{Threats to validity}
\label{sec:threats}
The limited sample size of tickets used in this research is the major threat to its validity. %It may happen, that only with 100 seemingly random tickets, there may be a prior unknown tendency. This is in fact similar to~\cite{sliwerski2005changes}, where the trend indicates that most bugs are fixed on Fridays.

@@

\section{Conclusions and Future Work}
\label{sec:conclusions}

In the preliminary results we have observed that the current premise, based on the SZZ algorithm, does not hold in all cases. Around half of the previous commits analyzed have been identified as responsible for inserting the line with the bug. Thus, the articles based on SZZ algorithm may be based on a wrong assumption. However, a larger number of tickets has to be studied to ascertain that our findings can be generalized. Our idea is contribute with this study in the knowledge about the responsibility practiced by the previous commit in a bug, helping to the software engineering community in the code review process. FIXME: aclarar esta frase que no me queda clara: Our idea is propose a reinterpretation in the responsibility practiced by the previous commit in a bug.

In the next months, we will carry out another empirical study with a larger sample size to prove that our results can be generalized. In this way, with a larger population we may be able to find certain patterns that we are now omitting. Furthermore, we extend this study to other projects to ascertain that what we have found occurs regardless of the project analyzed, because the OpenStack may be a special project, where the code is evolving continuously. In fact, we can access a huge database of other projects such as Eclipse or Mozilla that will allow us analyze this assumption, and where we will use statistical analysis to compare the results obtained in the different projects.

In addition, we have developed a tool that automatizes the first stage, displaying all the information used in the analysis in a web page\footnote{\url{http://bugtracking.libresoft.es}}, decreasing the time used in the analysis for the first stage. The future work with the tool will focus on improving and automating the second stage.

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This section is optional; it is a location for you
to acknowledge grants, funding, editing assistance and
what have you.  In the present case, for example, the
authors would like to thank Gerald Murray of ACM for
his help in codifying this \textit{Author's Guide}
and the \textbf{.cls} and \textbf{.tex} files that it describes.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\end{document}

>>>>

\section{Introduction}
\label{sec:introduction}
%How to plan to apply the knowledge in a way that can benefit software engineers.
%What are the anticipated contributions of the work?  How will you evaluate them to demonstrate usefulness?

%Many efforts on how and why bugs are introduced in the software source code are underway in the software engineering research community. Software source code is affected by many changes, many of them due to failure of the software because of emergent bugs. Concepts such as bug seeding help us to find how and where a bug was inserted in the source code, and which is the responsible line for a bug~\cite{zimmermann2005mining}.

%The current body of knowledge presents a wide collection of tools~\cite{kim2006automatic,fejzer2015supporting} that analyzes the code, and suggest where a potential bug can be found. Other publications describe how to find an error in the source code~\cite{yin2011fixes,zimmermann2006mining}.

%These articles are based on an implicit assumption: that the line that contains the error was caused by the immediately previous commit as in~\cite{kim2008classifying}, where the authors introduce a new technique to classify changes into two main categories, buggy or clean. In fact they assume the last commit contains the line with the bug. Other authors~\cite{sliwerski2005changes} do not even mention who is the responsible, because they (implicitly) assume the fixed bugs were introduced in the previous commits.

We refer to such \textit{previous commit} that the commit immediately before the bug fix.

%While performing research on the topic, we did not find any empirical evidence that supported this assumption, so we decided to investigate its validity in the case of a large project, such as the OpenStack free/open source cloud computing infrastructure software.

%In order to investigate if this assumption is valid, we formulate following research questions:
In this paper, we attempt to address the following research question regarding who introduced the bug in the source code.
\begin{itemize}
    \item RQ1 : How can tickets which are bug reports be differentiated from those that are not?
    \item RQ2:  How often is the bug caused in the previous commit?
\end{itemize}

The remainder of this paper is structured as follows. First, we present the motivations that support our study,  explaining the current problem in section~\ref{sec:assumption}. Then, Section~\ref{sec:caseStudy} describes our empirical study in an open source project such as OpenStack, followed by the results in Section~\ref{sec:results}. Section~\ref{sec:discussion} discusses potential applications and improvements of our approach. Section~\ref{sec:threats} reports threats to validity. Finally, Section~\ref{sec:related} presenst the actual body of knowdeadge about who caused the bug and Section~\ref{sec:conclusions} concludes the article.

\section{The Current Assumption}
\label{sec:assumption}

- Problem of missclassification\\
- Problem of little empirical evidence about the hypotesis.\\

@@

Each ticket has an id unique in Launchpad, which will be referred as \textit{n\_ticket}. Given its id, all information about the bug is publicly available in the issues tracking system\footnote{\url{https://bugs.launchpad.net/cinder/+bug/n_ticket}}. OpenStack uses Gerrit as code review system to see the evolution of each bug report\footnote{\url{https://review.openstack.org/ }}. Specifically we found the code review for each \textit{'n\_ticket'}\footnote{\url{https://review.openstack.org/#/c/n_review}}, where \textit{'n\_review'} is the review unique id for each \textit{'n\_ticket'}. In the code review all the information about the patchset that fixed the bug is shown.

@@

The researchers found main differences to extract data or to classify. In case of disagreement about the ticket classification among researchers, four criteria were used:
\begin{itemize}
    \item When there are only test files in the ticket, we classified it as note being a bug report. Test files in a ticket will not be analyzed, they are indispensables and used as testing method to determine whether the code is fit for use. Sometimes the developers inserted the bug only in the test files, in these cases the ticket was not considered as bug report because the software works as expected only failed the test.
    \item When the title described a new feature, our criteria indicated that it was not a bug report. New features are not considered bug reports, because there is no failure. The optimization, deletion of a dead code or the implementation of new characteristics are included in this criteria. 
    \item When the title described the program as not working as expected, our criteria indicated that it was a bug report. Sometimes the bug is not in a main function which prevents \texttt{Cinder} from working, because a developer has considered it an important bug, although not relatively important. But it is not working as he/she expected. 
    \item When the title described that updates were required, our criteria indicated that it was a bug report. We consider all tickets that require updating as bug reports, because updating a software hints to the software not operating as expected. 
\end{itemize}

Sometimes we were unable to answer all the questions due to having insufficient data or because of the complexity of the issue. In this case, the ticket was classified into the \textit{Undecided} group.

@@

\begin{table*}[htb]
\begin{center} {\footnotesize
\caption{ Concordance between each developer in each repository}
\label{tab:3}
\begin{tabular}{llllll}
\toprule[0.3mm]%{\smallskip}
  & Nova\kern 1pc & Cinder\kern 1pc & Horizon\kern 1pc & Neutron\kern 1pc & Total\\\hline
D1 and D2  \kern 1pc & (44/63) 70\%\kern 1pc & (40/52) 77\%\kern 1pc & (37/62) 60\%\kern 1pc & - \kern 1pc& 68\% \\
D1 and D3  \kern 1pc &  -\kern 1pc & (46/63) 73\%\kern 1pc & (48/63) 76\%\kern 1pc & (26/42) 62\%\kern 1pc & 71 \% \\
D2 and D3  \kern 1pc & (41/62) 66\%\kern 1pc & (10/10) 100\%\kern 1pc  & - \kern 1pc& -\kern 1pc  &  71\% \\
\bottomrule[0.3mm]
\end{tabular} }
\end{center}
\end{table*}

The table ~\ref{tab:3} shows that the concordance of the developers is high but, also demonstrate the difficulty to classify tickets as bug report or as not bug report, because each developer can have different ideas about a specific ticket. The concordance between the developers could be higer if they were expert in the project.

@@

\subsubsection{BugTracking: The tool used}
\label{sec:tool}
The tool was designed to solve the problem of missclassified, providing the researcher with all the relevant information needed to decide if an issue belongs to a bug report or not. The tool is available at\footnote{\url{bugtracking.libresoft.es}} and extracts automatically tickets from the project's repository, and offers a web-based interface which allows for collaboration, traceability and transparency of the identification of bug reports.
The webpage provide us different functionalities depend on in which tab we are, next we explain these functionalities.
\begin{enumerate}
  \item Tab Repository: In this tab we choose which repository of OpenStack we want analyze. Currently the tool supports the four principal repositories: Cinder, Nova, Neutron and Horizon, in which there is more activity.
  \item Tab Analyze: Is the Tab showed in \ref{fig:1} where the user select/insert an identifyer of a ticket and analyze with all the data displayed if the ticket are a bug report or not.
  \item Tab Statistics: This tab collects the data saved in the user's repository in GitHub after analyze each ticket, and displays a table with the number of tickets classified as \textit{Bug Report},\textit{Not Bug Report} and \textit{Undecided} in the repository and from each developer involved in the analysis, which name has to be selected previously.
  \item Tab Modify: In this tab, the user can see all his data saved in the GitHub repository and modify the content of the file that he wants, in case of have inserted a mistake during the analysis.
\end{enumerate}

@@

At this stage, we got a list with all the previous commits, which could be where the bug was introduced. We  identifyed a total of 348 previous commits which can be responsible for inserting the line with the bug. When there are more than one commit implicated in the same file is because the bug was inserted in different lines of different commits, but not everyone has to be responsible for the commit, sometimes the previous commit copied lines from its previous commit or inserted comments and blank spaces. After the analysis the responsible can be only one of them, more than one or none.

We analyzed a total of 209 tickets in which there were 348 previous commit, which we had to classify into one of the following groups, according to the responsability of the previous commit in the bug fix:
\begin{enumerate}
  \item It is responsible, when we are sure that the commit inserted the line with the bug.
  \item It is not responsible, when we are sure that the commit dind't insert the line with the bug.
  \item Undecided, when we cannot be sure if the commit is responsible due to our few knowleadge about the project or when the bug fix only added lines, complicating the analysis.
\end{enumerate}

@@

%To analyze the lines of the files involved, we used therefore the \texttt{diff} command to display line-by-line difference between the file before and after the bug fix commit. \texttt{diff} is well-known algorithm, extensively explained in the research literature~\cite{ukkonen1985algorithms,myers1986ano}, which is included in any source code management system. \texttt{diff} examines both files and returns the differences found between them, showing the line number.% the necessary modifications which should be done in order to the files match. the differences found between them,showing the line number. %FIXME: de aqui en adelante no entiendo la frase. need to be made for first file and second file to match, that is, returns the differences found between them.

After analayzed all the previous commit involved in the 209 Bug reports, we have discovered that not all the previous commits inserted the bug. This expecific project, which is continuosly evolving, presents some cases in which the bug was introduced by other actions. A clear example is the changes in called APIs, after the addition of a new feauture the called API fails, due to it requires an extra argument, but in the API there is not any bug.

Other example is shows in the commit log of a bug fix \ref{fig:5}, the name of a variable changed in the new version causing a failure. This change due to the new requirements in the version doesn't implicate that the previous commit was who inserted the bug, because until the new version the system doesn't fail.

\begin{figure}[htb]
\centering
\includegraphics[height=2.3cm]{UpdateFixBug.png}
\caption{Description of the bug-fix commit}
\label{fig:5}       % Give a unique label
\end{figure}

\subsubsection{Discarting False Positives}
\label{sec:discarting}
The classification of the previous commits according to its responsability has some noise that we had to delete. These previous commits that changed the format, added blank lines, changed comments or copied lines from the previous commit were discarted due to they were not responsibles for cause the bug.

@@

\subsection{Fist Stage}
\label{sec:resultsFS}
We have manually analyzed 459 different tickets with support of the present tool, 125 from Cinder, 125 fron Nova, 125 from Horizon and 84 from Neutron. The table \ref{tab:1} show the percentage of each researcher after analyzing the tickets, 417 tickets were analyzed by two different researchers,

@@

\begin{table}[htb]
\begin{center} {\footnotesize
\caption{ Probability of cause the bug depending on how many previous commits had the bug report}
\label{secondStage}
\begin{tabular}{lcc}
\toprule[0.3mm]
  & \multicolumn{1}{c}{After} & \multicolumn{1}{c}{Before} \\
  & \multicolumn{1}{c}{False Negative} & \multicolumn{1}{c}{False Negative} \\\hline
\raisebox{1ex}{Responsible} & 152 & 152 \\[0ex]
\raisebox{1ex}{Not responsible} & 154 & 114 \\[0ex]
\raisebox{1ex}{Undecided} & 42 & 42 \\[0ex]
\bottomrule[0.3mm]
\end{tabular} }
\end{center}
\end{table}

58 tickets with more than one previous commit and 131 with only one previous commit
\begin{table}[htb]
\begin{center} {\footnotesize
\caption{ Probability of cause the bug depending on how many previous commits had the bug report}
\label{secondStage}
\begin{tabular}{lcc}
\toprule[0.3mm]
  & \multicolumn{1}{c}{One previous } & \multicolumn{1}{c}{More than one previous} \\
  & \multicolumn{1}{c}{commit} & \multicolumn{1}{c}{commit} \\\hline
\raisebox{1ex}{Responsible} & 65\% & 86\% \\[0ex]
\raisebox{1ex}{Not responsible} & 30\% & 82\%\\[0ex]
\raisebox{1ex}{Undecided} & 36\% & 11\%\\[0ex]
\bottomrule[0.3mm]
\end{tabular} }
\end{center}
\end{table}

@@

\section{Threats to validity}
\label{sec:threats}
The limited sample size of tickets used in this research is the major threat to its validity. %It may happen, that only with 100 seemingly random tickets, there may be a prior unknown tendency. This is in fact similar to~\cite{sliwerski2005changes}, where the trend indicates that most bugs are fixed on Fridays.

@@

\section{Related Work}
\label{sec:related}
First SZZ\\
Second Improvement of SZZ\\
Then SZZ revisited\\
Then Buginnings\\
Finally our idea.

\section{Conclusions}
\label{sec:conclusions}

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
We thank the two phd students, Dorealda Dalipaj and Nelson Sekitoleko, that participated differentiating Bug report from the others. Also, we thank Bitergia \footnote{\url{http://bitergia.com/}} to explain its available database of OpenStack. 
Finally,thanks the Spanish Goverment because all authors are funded in part by it, through project TIN2014-59400-R.

\nocite{*}
%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\end{document}
